A Survey on Ordered Binary Decision Diagrams

### 2015-09-11 paper.tex
Add content Compose operation

This operation is merely based upon calls to \textit{Apply} and \textit{Restrict}.
Utilizing \textit{Shannon's expansion}, Bryant~\cite{BRYANT86} formulated the
composition of two functions $f_1$ and $f_2$ as
\begin{center}
$
f_1|_{x=f_2}=
f_2 \land f_1|_{x_i=1} \lor \overline{f_2} \land f_1|_{x_i=0}
$
\end{center}\tbr

>>>>

This operation is merely based upon calls to \textit{Apply} and \textit{Restrict}.
Utilizing \textit{Shannon's expansion}, Bryant~\cite{BRYANT86} formulated the
composition of two functions $f_1$ and $f_2$ as
\begin{center}
$
f_1|_{x=f_2}=
f_2 \land f_1|_{x_i=1} \lor \overline{f_2} \land f_1|_{x_i=0}
$
\end{center}

However, this would result in an algorithm having a time complexity of 
$O\left(|V_{f_1}|^2 \cdot |V_{f_2}|^2\right)$. Therefore, Bryant~\cite{BRYANT86}
already proposed to extend the \textit{Apply} operation to support ternary
operations and then use the equivalent \textit{if-then-else} (\textit{ITE})
representation:
\begin{center}
$
ITE\left(f_2, f_1|_{x_i=1}, f_1|_{x_i=0}\right) \equiv
f_2 \land f_1|_{x_i=1} \lor \overline{f_2} \land f_1|_{x_i=0}
$
\end{center}

\noindent
The time complexity then improves to be
$O\left(|V_{f_1}|^2 \cdot |V_{f_2}|\right)$~\cite{BRYANT86}. \tbr
